{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-31 Paper/main.tex
Some fpcr theory

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]\\
			& \approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
		\end{split}
	\end{equation}

	Using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.

	\begin{equation}
		\begin{split}
			Z_{j, k}^m & =  b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L\\
		\end{split}
	\end{equation}

	For notational purposes in this paper we define the following convention:

>>>>

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right] \approx \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right]
		\end{split}
	\end{equation}

	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
